Binary companions of evolved stars in \apogee\ \DR: \\ Search method and catalog of $\sim$5,000 companions

### 2018-04-24 paper/1-catalog/twoface-catalog.tex
thanks
git hash
Ref tidal circ paper

The period-eccentricity plot (upper left panel in
\figurename~\ref{fig:logg-teff-p-e}) shows a clear signature of tidal
circularization: such plots for main sequence stars typically show a more
distinct circularization period, below which the majority of stars have
eccentricities close to zero.
Here, we see that close to $P\approx 10~\textrm{day}$ the majority of companion
orbits appear to be circular, but between 10--100~days there appears to be a
gradual decrease in eccentricity rather than a sharp transition.
This is likely because the primary stars in this sample have a large range in
surface gravities and therefore a large range in stellar radii (see lower right
panel).

@@

The source code for this project is open source and available from
\url{https://github.com/adrn/TwoFace} under the MIT open source software
license.

@@

It is a pleasure to thank
Kevin Covey (WWU),
Marla Geha (Yale),
Marina Kounkel (WWU),
Keith Hawkins (Columbia),
Melissa Ness (Columbia/Flatiron),
David Spergel (Princeton/Flatiron),
and Yuan-Sen Ting (Princeton).

>>>>

The period-eccentricity plot (upper left panel in
\figurename~\ref{fig:logg-teff-p-e}) shows a clear signature of tidal
circularization: such plots for main sequence stars typically show a more
distinct circularization period, below which the majority of stars have
eccentricities close to zero.
Here, we see that close to $P\approx 10~\textrm{day}$ the majority of companion
orbits appear to be circular, but between 10--100~days there appears to be a
gradual decrease in eccentricity rather than a sharp transition.
This is likely because the primary stars in this sample have a large range in
surface gravities and therefore a large range in stellar radii (see lower right
panel); this result is explored in more detail in companion work
(\citealt{Circularization:2018}).

@@

The source code for this project is open source and available from
\url{https://github.com/adrn/TwoFace} under the MIT open source software
license.
This paper version was generated with Git commit \texttt{\githash\,(\gitdate)}.

@@

It is a pleasure to thank
Kevin Covey (WWU),
Marla Geha (Yale),
Marina Kounkel (WWU),
Keith Hawkins (Columbia),
Melissa Ness (Columbia/Flatiron),
David Spergel (Princeton/Flatiron),
and Yuan-Sen Ting (Princeton).
We thank the anonymous referee for constructive comments that improved this
manuscript.
